Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-09 paper/disc20clustering.tex
a same to the same

\begin{proof}
	Fix any online algorithm \ALG{}.
	Let $I(C)$ denote the cluster where nodes of the ground set $C$ are located in the initial configuration.
	If $C$ contains nodes that originate from different clusters, $I(C)$ is undefined.
	Throughout the construction, we maintain ground sets for each node.
	Initially all nodes are \emph{isolated}.
	First, we create a ground set $B$ of $k-1$ nodes on an arbitrarily chosen cluster (the nodes  are already collocated).
	%We never dismiss any constructed ground set.
	Each cluster hosts exactly $k$ nodes, and in any configuration a single isolated node resides in $S$.
	We say that this isolated node that accompanies the ground set $B$ is \emph{special}.
	We denote the first special node by $x_0$.

@@

In our algorithms, a~\emph{component} is a subset of frequently communicating nodes.
We maintain all nodes of a component always collocated in a same cluster~\cite{repartition-disc}.
When we  move a~node, we move the whole component that contains it.
We maintain a balanced partition of our components,
a reminiscent of partitioning given integers into sets of equal sum \cite{integer-partitions-book}.
In contrast, our partition is time-varying:  two components are merged into one component once they communicate, and we adjust the partition accordingly.

@@

\textbf{The charging scheme.}
Consider two  pairs that share a same node, 
i.e.~\emph{intersecting pairs},
and the set of requests that causes the collocation of both pairs,
at some  times during  $[1,m]$.
%i.e.~the entire duration of the sequence.
Observe that \OPT must pay a non-zero cost
for these requests over the entire $\sigma$,
since it cannot have both pairs initially collocated.
However,
we can charge the whole cost to \OPT only the first time \RM collocates a pair,
and not at any consequent time when \RM collocates it a second time.
Otherwise,
 \OPT is possibly charged for a same cost repeatedly.
For this reason,
we charge \OPT a cost inflicted by a pair,
if and only if  \OPT incurs that cost after the latest separation of the pair by \RM.
%%

>>>>

\begin{proof}
	Fix any online algorithm \ALG{}.
	Let $I(C)$ denote the cluster where nodes of the ground set $C$ are located in the initial configuration.
	If $C$ contains nodes that originate from different clusters, $I(C)$ is undefined.
	Throughout the construction, we maintain ground sets for each node.
	Initially all nodes are isolated (i.e., in ground sets of size $1$).
	First, we create a ground set $B$ of $k-1$ nodes on an arbitrarily chosen cluster (the nodes  are already collocated).
	%We never dismiss any constructed ground set.
	Each cluster hosts exactly $k$ nodes, and in any configuration a single isolated node resides in $S$.
	We say that this isolated node that accompanies the ground set $B$ is \emph{special}.
	We denote the first special node by $x_0$.

@@

In our algorithms, a~\emph{component} is a subset of frequently communicating nodes.
We maintain all nodes of a component always collocated in the same cluster~\cite{repartition-disc}.
When we  move a~node, we move the whole component that contains it.
We maintain a balanced partition of our components,
a reminiscent of partitioning given integers into sets of equal sum \cite{integer-partitions-book}.
In contrast, our partition is time-varying:  two components are merged into one component once they communicate, and we adjust the partition accordingly.

@@

\textbf{The charging scheme.}
Consider two  pairs that share the same node, 
i.e.~\emph{intersecting pairs},
and the set of requests that causes the collocation of both pairs,
at some  times during  $[1,m]$.
%i.e.~the entire duration of the sequence.
Observe that \OPT must pay a non-zero cost
for these requests over the entire $\sigma$,
since it cannot have both pairs initially collocated.
However,
we can charge the whole cost to \OPT only the first time \RM collocates a pair,
and not at any consequent time when \RM collocates it a second time.
Otherwise,
 \OPT is possibly charged for the same cost repeatedly.
For this reason,
we charge \OPT a cost inflicted by a pair,
if and only if  \OPT incurs that cost after the latest separation of the pair by \RM.
%%
